Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-11-14 doc/JFLA2022/paper.tex
minor changes

 Our new proof of Theorem~\ref{thm3} is based on a systematic study of strictly decreasing sequences of ordinals below $\epsilon_0$, borrowed from Ketonen and Solovay~\cite{KS81}, and the formalization of which is described  in chapters 5 and 6 of~\cite{HydraBook}.

We also study the number of steps of a battle:
Let $\alpha<\epsilon_0$ be an ordinal. 
We prove that  the number of steps of the battle starting with
$\alpha$ at step $i$ is greater or equal than
$H'_\alpha(i)-i$, where $H'$ is a slight variant of the Hardy hierarchy of rapidly growing functions~\cite{BW85, KS81, Promel2013, Wainer1970}.  The function $H'_\alpha$ is defined by transfinite recursion over $\alpha$ on Figures~\ref{fig:hardy-math}
and~\ref{fig:Hprime}.

>>>>

 Our new proof of Theorem~\ref{thm3} is based on a systematic study of strictly decreasing sequences of ordinals below $\epsilon_0$, borrowed from Ketonen and Solovay~\cite{KS81}, and the formalization of which is described in detail  in chapters 5 and 6 of~\cite{HydraBook}.

 Besides  Theorem~\ref{thm3}, we study also the number of steps of a battle:
Let $\alpha<\epsilon_0$ be an ordinal. 
We prove that  the number of steps of the battle starting with
$\alpha$ at step $i$ is greater or equal than
$H'_\alpha(i)-i$, where $H'$ is a slight variant of the Hardy hierarchy of rapidly growing functions~\cite{BW85, KS81, Promel2013, Wainer1970}.  The function $H'_\alpha$ is defined by transfinite recursion over $\alpha$ on Figures~\ref{fig:hardy-math}
and~\ref{fig:Hprime}.
